Rapid Georectification of Pushbroom Hyperspectral Imagery for Real Time Processing by an Autonomous Aerial Vehicle

### 2023-08-29 paper/paper.tex

\begin{figure}[H]
    \centering
    \includegraphics[width=10.5cm]{./assets/georectification.svg}
    \caption{Georectification procedure.}
    \label{fig:georectification}
\end{figure}

@@

\textbf{NOTE} Stuff to do in this section:
\begin{itemize}
    \item  Create table with processing timings for each step on a typical HSI
    \item Create second table comparing time for full processing including resampling to a variety of scales (e.g. 5 cm, 10 cm, 25 cm) We will want a version of the processing function that does not include the uncertainties and the spectral indices
    \item create additional table showing size of each of the data producs and their step in the pipeline (ending with a dataproduct like the NDVI)
    \item Create a figure showing the georeferenced image on top of the satellite background 
    \item Create another figure of the entire map with a spectral index applied to one of the dye-release datasets (to demonstrate use for real-time application like oil-spill)
    \item create a figure of a sample HSI datacube in 3-d like from the previous paper with the rgb image on the top. 
\end{itemize}

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=10.5cm]{./assets/georectification.eps}
    \caption{Visual representation of scan-line geometry for the drone based hyperspectral imaging platform.}
    \label{fig:georectification}
\end{figure}

@@

\textbf{NOTE} Stuff to do in this section:
\begin{itemize}
    \item  Create table with processing timings for each step on a typical HSI
    \item Create second table comparing time for full processing including resampling to a variety of scales (e.g. 5 cm, 10 cm, 25 cm) We will want a version of the processing function that does not include the uncertainties and the spectral indices
    \item create pipeline visualization showing size of each of the data products and their step in the pipeline (ending with a dataproduct like the NDVI)
    \item Create a figure showing the georeferenced image on top of the satellite background 
    \item Create another figure of the entire map with a spectral index applied to one of the dye-release datasets (to demonstrate use for real-time application like oil-spill)
    \item create a figure of a sample HSI datacube in 3-d like from the previous paper with the rgb image on the top. 
\end{itemize}
